mlr3spatiotempcv: Spatiotemporal Resampling Methods for 'mlr3

### 2020-11-19 joss/joss.Rmd
reference fix

At the time of writing, various R packages implementing different spatiotemporal partitioning strategies exist: CAST [@cast], blockCV [@blockCV] or sperrorest [@brenning2012].
There are some resampling methods used in scientific studies for which the source code is either not available or a different programming language has been used [@roberts2017, @pohjankukka2017]

>>>>

At the time of writing, various R packages implementing different spatiotemporal partitioning strategies exist: CAST [@cast], blockCV [@blockCV] or sperrorest [@brenning2012].
There are some resampling methods used in scientific studies for which the source code is either not available or a different programming language has been used [@roberts2017; @pohjankukka2017]
